\documentclass[11pt]{article}
\usepackage{common}
\title{MultiDocument Text Summarization}
\author{Kevin Eskici (keskici@college.harvard.edu) \and Luis A. Perez (luis.perez.live@gmail.com)\\
Computer Science 182, Harvard University}
\begin{document}
\maketitle{}


\section{Introduction}

A description of the purpose, goals, and scope of your system or
empirical investigation.  You should include references to papers you
read on which your project and any algorithms you used are
based. Include a discussion of whether you adapted a published
algorithm or devised a new one, the range of problems and issues you
addressed, and the relation of these problems and issues to the
techniques and ideas covered in the course.

\section{Background}


\section{Related Work}

For instance, \cite{hochreiter1997long}.


\section{Body 1}

A clear specification of the algorithm(s) you used and a description
of the main data structures in the implementation. Include a
discussion of any details of the algorithm that were not in the
published paper(s) that formed the basis of your implementation. A
reader should be able to reconstruct and verify your work from reading
your paper.

\section{Body 2}


\begin{algorithm}
  \begin{algorithmic}
    \Procedure{MyAlgorithm}{$b$}
    \State{$a \gets 10$}
    \EndProcedure{}
  \end{algorithmic}
  \caption{Here is the algorithm.}
\end{algorithm}



\section{Experiments}
Analysis, evaluation, and critique of the algorithm and your
implementation. Include a description of the testing data you used and
a discussion of examples that illustrate major features of your
system. Testing is a critical part of system construction, and the
scope of your testing will be an important component in our
evaluation. Discuss what you learned from the implementation.

\begin{table}
  \centering
  \begin{tabular}{ll}
    \toprule
    & Score \\
    \midrule
    Approach 1 & \\
    Approach 2 & \\
    \bottomrule
  \end{tabular}
  \caption{Description of the results.}
\end{table}

\subsection{Methods and Models}


\subsection{Results}

 For algorithm-comparison projects: a section reporting empirical comparison results preferably presented graphically.


\subsection{Discussion}


\appendix

\section{Program Trace}

Appendix 1 – A trace of the program showing how it handles key examples or some other demonstration of the program in action.

\section{System Description}

 Appendix 2 – A clear description of how to use your system and how to generate the output you discussed in the write-up and the example transcript in Appendix 1. N.B.: The teaching staff must be able to run your system.

\section{Group Makeup}

 Appendix 3 – A list of each project participant and that
participant’s contributions to the project. If the division of work
varies significantly from the project proposal, provide a brief
explanation.  Your code should be clearly documented. 



\bibliographystyle{plain} 
\bibliography{../references}

\end{document}
